---
title: "Gymastics Case Study, Part 2"
author: "425/625"
date: "September 06, 2023"
output:
  pdf_document: default
  word_document: default
urlcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Predicting outcomes for a set of 5-person teams

In this part you will focus on predicting outcomes (scores, medals, probability of medaling, or other outcomes of interest) for a single set of 5-person teams for the countries in the competition.  

1. Determine a reasonable set of countries that will compete in the Olympics
2. Determine a reasonable 5-person team for every country. This does not have to be optimal at this point, just reasonable.  
3. Determine the additional gymnasts, not from one of the qualifying countries, that will qualify for the Olympics. Don't spend a lot of time on these first three points. Just get something reasonable that you can use in #4.
4. Assuming these are the 5-person teams, simulate, or otherwise determine the likely outcomes of 

    a. the qualifying stage, 
    b. team all-around, 
    c. individual all-around, and 
    d. individual event finals. 

Do this for men's and women's competitions. 

## Read the dataset from data_2022_2023.csv
  
```{r}
  # Read the dataset from data/data_2022_2023.csv
  data <- read.csv("data/data_2022_2023.csv")
  # print the size of the data
  print(dim(data))

  # Select the contry column from the data
  country <- data$Country
  # Select 12 contries from the data. Note that we should ignore repeated entries.
  country <- unique(country)
  country <- country[1:12]
  # Select the rows in the data that matches the contries we selected
  data <- data[data$Country %in% country,]
  # print the size of the data
  print(dim(data))

  # Split the data based on the country
  data_split <- split(data, data$Country)
```

## For each country, select 5 gymnasts for the team

```{r}
  # For each data frame in the list, select the top 5 gymnasts based on the total score
  # write a function that returns the top k gymnasts based on the total score
  top_k <- function(df, k){
    # delete the rows that have NA in the total score column
    df <- df[!is.na(df$Total), ]
    # split the data based on the athlete's LastName and FirstName
    df_split <- split(df, df$LastName)
    # For each data frame (corresponding to each individual athlete) in the list, calculate the average total score
    total_sc_split <- lapply(df_split, function(x) mean(x$Total))
    # get a name list of the athletes
    last_name_list <- lapply(df_split, function(x) x$LastName[1])
    first_name_list <- lapply(df_split, function(x) x$FirstName[1])
    # create a data frame that contains the average total score and the name of the athlete, the data frame should contains 3 columns with the name "LastName", "FirstName", and "Score"
    df_new <- data.frame(last_name_list, first_name_list, total_sc_split)
    # rename the columns
    colnames(df_new) <- c("LastName", "FirstName", "Score")
    # sort the data frame based on the average total score
    df_new <- df_new[order(df_new$Score, decreasing = TRUE),]
    # select the top k athletes
    df_new <- df_new[1:k,]
  }
```

```{r}
  # create a list that contains the top 5 gymnasts for each country
  top_5_list <- lapply(data_split, function(x) top_k(x, 5))
  # print the list
  print(top_5_list)
```